Reproducible development environments with rix

### 2023-11-11 paper.qmd
Update paper.qmd

---
title: "A Short Demo Article: Regression Models for Count Data in R"
format:
    jss-pdf:
        keep-tex: true
    jss-html: default
author:
  - name: Achim Zeileis
    affiliations:
      - name: Universität Innsbruck
        department: Department of Statistics
        address: Universitätsstr. 15
        city: Innsbruck
        country: Austria
        postal-code: 6020
      - Journal of Statistical Software
    orcid: 0000-0003-0918-3766
    email: Achim.Zeileis@R-project.org
    url: https://www.zeileis.org/
  - name: Second  Author
    affiliations:
      - Plus Affiliation
abstract: |
  This short article illustrates how to write a manuscript for the
  _Journal of Statistical Software_ (JSS) using its {{< latex >}} style files.
  Generally, we ask to follow JSS's style guide and FAQs precisely. Also,
  it is recommended to keep the {{< latex >}} code as simple as possible,
  i.e., avoid inclusion of packages/commands that are not necessary.
  For outlining the typical structure of a JSS article some brief text snippets are employed that have been inspired by @ZeileisKleiberJackman2008, discussing count data regression in [R]{.proglang}. Editorial comments and instructions are marked by vertical bars.

>>>>

---
title: "Reproducible development environments with rix"
format:
    jss-pdf:
        keep-tex: true
    jss-html: default
author:
  - name: Bruno Rodrigues 
    affiliations:
      - name: Ministry of higher education and research, Luxembourg 
        department: Department of Statistics
        address: 18, Montée de la Pétrusse
        city: Luxembourg 
        country: Luxembourg 
        postal-code: 2327
      - Journal of Statistical Software
    orcid: 0000-0002-3211-3689
    email: bruno@brodrigues.co
    url: https://www.brodrigues.co 
  - name: Philipp Baumann
    affiliations:
      - Plus Affiliation
abstract: |
  This short article illustrates how to write a manuscript for the
  _Journal of Statistical Software_ (JSS) using its {{< latex >}} style files.
  Generally, we ask to follow JSS's style guide and FAQs precisely. Also,
  it is recommended to keep the {{< latex >}} code as simple as possible,
  i.e., avoid inclusion of packages/commands that are not necessary.
  For outlining the typical structure of a JSS article some brief text snippets are employed that have been inspired by @ZeileisKleiberJackman2008, discussing count data regression in [R]{.proglang}. Editorial comments and instructions are marked by vertical bars.
